\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-22 document/ms.tex
figure refs

The difference between the observed radius distributions apparent in Figure \ref{obs-dist}
can be attributed to the drop off in sensitivity of our search at small planet
radius depicted in Figure \ref{completeness}.  The \kepler\ survey, on the other 
hand, has increasing sensitivity to smaller planets due to the addition of multiple 
transits at shorter period.

@@

\newpage
\section{Empirical search completeness}\sectlabel{completeness}

@@

\newpage
\bibliography{peerless}

>>>>

The difference between the observed radius distributions apparent in
\dfmfig{obs-dist} can be attributed to the drop off in sensitivity of our
search at small planet radius depicted in \dfmfig{completeness}.
The \kepler\ survey, on the other hand, has increasing sensitivity to smaller
planets due to the addition of multiple transits at shorter period.

@@

\section{Empirical search completeness}\sectlabel{completeness}

@@

% \newpage
\bibliography{peerless}
